Evaluating Model Performances

### 2019-06-30 Scripts/evaluating_model_performances_rf.Rmd
added other version of plot

## Plots

@@

>>>>

# Line Plots V1

@@

# Line Plots V2

```{r}
x <- ggplot(all_rfperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(CL ~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("Resolution") + ylab("MCC") + ylim(-.1,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     strip.text.x = element_text(size = 15),
     strip.text.y = element_text(size = 15),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20),
     legend.position="bottom")

#figure <- ggarrange(x,
#                ncol = 1, nrow = 1, 
#                common.legend = TRUE, 
#                legend = "bottom")
#figure
#annotate_figure(figure,
#    bottom = text_grob("Resolution", color = "black", size = 20),
#    left = text_grob("MCC", color = "black", rot = 90, size=20)
#)
